An excess of positive results: Comparing the standard Psychology literature with Registered Reports

### 2020-02-05 preprint/positive_results_SRs_RRs.Rmd

## Disclosures
### Data, materials, and online resources
Data and code necessary to reproduce all analyses reported here, as well as the [Appendix](https://osf.io/qw798/), the [preregistration](https://osf.io/sy927/), and additional supplementary files, are available at <https://osf.io/dbhgr>. The manuscript including figures and statistical analyses, the [Appendix](https://osf.io/qw798/), and the [codebook](https://osf.io/6jrkz/) available in the supplement were created using RStudio [1.2.5019, @RStudioTeam2019] and `r my_citation`.

>>>>

## Disclosures
### Data, materials, and online resources
[Data](https://osf.io/aqr2s/) and code necessary to reproduce all analyses reported here, as well as the [Appendix](https://osf.io/qw798/), the [preregistration](https://osf.io/sy927/), and additional supplementary files, are available at <https://osf.io/dbhgr>. 
The manuscript, including figures and statistical analyses, the [Appendix](https://osf.io/qw798/), and the [codebook](https://osf.io/6jrkz/) available in the supplement were created using RStudio [1.2.5019, @RStudioTeam2019] and `r my_citation`.
